CixPAG-IMD-Tx

### 2016-10-20 CixPAG/CixPAG-imd.Rmd
small fix

Trend in the men summer maximum daily maximum temperature

```{r}
map(Tx.maxjja,FUN='trend',new=FALSE)
```

@@

```{r}
predictor <- retrieve('air.mon.mean.nc',lon=c(60,100),lat=c(0,25))
predictor <- annual(subset(predictor,it='jja'),nmin=3)
eof.X <- EOF(predictor,n=10)
plot(eof.X,new=FALSE)
```

@@

```{r}
class(eof.Y) <- c("eof", "field", "season", "zoo") # Fix some incorrect settings
class(eof.X) <- c("eof", "field", "season", "zoo") # Fix some incorrect settings
index(eof.Y) <- as.Date(paste(year(eof.Y),'-07-01',sep=''))
index(eof.X) <- as.Date(paste(year(eof.X),'-07-01',sep=''))
ds.test <- DS(eof.Y,eof.X,ip=1:6)
plot(ds.test,new=FALSE)
```

@@

```{r}
if (!file.exists('dse.Tx.jja.cixpag.rda')) {
    dse.Tx <- DSensemble.eof(eof.Y,eof.X,ip=1:6,it='jja',
                             predictor='air.mon.mean.nc',verbose=FALSE)
    save(dse.Tx,file='dse.Tx.jja.cixpag.rda')
} else load('dse.Tx.jja.cixpag.rda')
```

```{r}
## Present annual maximum daily maximum temperature from RCP4.5 ensemble mean
z0 <- map(dse.Tx,it=2010,new=FALSE)
## annual maximum daily maximum temperature for 2050 based on RCP4.5 ensemble mean
z1 <- map(dse.Tx,it=2050,new=FALSE)
## Projected change in annual maximum daily maximum temperature
dz <- z1-z0
dz <- attrcp(z1,dz)
attr(dz,'dimensions') <- attr(z1,'dimensions')
class(dz) <- class(z1)
map(dz,new=FALSE)
```

>>>>

Trend in the max summer maximum daily maximum temperature

```{r map_trend_tx}
map(Tx.maxjja,FUN='trend',new=FALSE)
```

@@

```{r predictor}
predictor <- retrieve('air.mon.mean.nc',lon=c(60,100),lat=c(0,25))
predictor <- annual(subset(predictor,it='jja'),nmin=3)
eof.X <- EOF(predictor,n=10)
plot(eof.X,new=FALSE)
```

@@

```{r test_downscaling}
class(eof.Y) <- c("eof", "field", "season", "zoo") # Fix some incorrect settings
class(eof.X) <- c("eof", "field", "season", "zoo") # Fix some incorrect settings
index(eof.Y) <- as.Date(paste(year(eof.Y),'-07-01',sep=''))
index(eof.X) <- as.Date(paste(year(eof.X),'-07-01',sep=''))
ds.test <- DS(eof.Y,eof.X,ip=1:6)
plot(ds.test,new=FALSE)
```

@@

```{r downscale_ensemble}
if (!file.exists('dse.Tx.jja.cixpag.rda')) {
    dse.Tx <- DSensemble.eof(eof.Y,eof.X,ip=1:6,it='jja',
                             predictor='air.mon.mean.nc',verbose=FALSE)
    save(dse.Tx,file='dse.Tx.jja.cixpag.rda')
} else load('dse.Tx.jja.cixpag.rda')
```

```{r show_maps}
## Present annual maximum daily maximum temperature from RCP4.5 ensemble mean
z0 <- map(dse.Tx,it=2010,new=FALSE,plot=FALSE)
## annual maximum daily maximum temperature for 2050 based on RCP4.5 ensemble mean
z1 <- map(dse.Tx,it=2050,new=FALSE,plot=FALSE)
## Projected change in annual maximum daily maximum temperature
dz <- z1-z0
dz <- attrcp(z1,dz)
attr(dz,'dimensions') <- attr(z1,'dimensions')
class(dz) <- class(z1)
map(dz,new=FALSE)
```
